SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
more on proof 3

Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$. This
means that $Pred(l,L_1^*)$ is satisfiable, but
$Pred(l,L_2^*)$ is not satisfiable, which is a contradiction; or as in the
invariant proof, there is a similar sequence with an OT $l_1$ that leads to
a contradiction.

@@

Figure~\ref{schema:smt-lib} shows the decomposition of the
predicate into a set of asserts, each encoding an elementary equality,
inequality, or a guard. 
The result (SAT or UNSAT) of the final \texttt{check-sat} command in
the translation () is then decoded.

@@

\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the logical
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} how to prove these two automata are bisimilar.

@@

@@

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{ActaXFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{\{\xrightarrow{a1}_P\}\\ a1\neq\delta(x)}
    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{
                        \{\xrightarrow{a2}_Q\},\\a2\neq\delta(x)
                        }
    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
    OT_4 & = \openrule{
                      \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{\{\xrightarrow{a3}_R\}
    	}
    {\ostate{11} \xrightarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``$P>>(Q>>R)$''}
  \label{schema:enable3bis}
\end{figure}

>>>>

Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$.
The fact that $l \in L_1^*$ means that $Pred_l$, with the information contained in $Assigns(L_1^*)$, is satisfiable, but also all the transitions $\{l_i\}_{i \in [1..n]}$ in a sequence
$s_0\xrightarrow{l_1}s_1\xrightarrow{l_2}...s_{n}\xrightarrow{l_{n+1}}s_{n+1}$ leading to this $l_{n+1}=l$.

Clearly all these $\{l_i\}_{i \in [1..n]}$ were also satisfiable and reachable in $L_2^0$ during the ``smart'' traversal, which did not use assignments. Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by algorithm \ref{alg3}; we argue that the specific instanciation of variables that makes $Pred(l,L_1^*)$ satisfiable was contained in $Assigns(L_2^0)$, and that if it were removed during one of the $Refine$ step in algorithm \ref{alg1}, then it would be remove similarily during algorithm \ref{alg3}. So we get a contradiction.

@@

Figure~\ref{schema:smt-lib} shows the decomposition of the
predicate into a set of asserts, each encoding an elementary equality,
inequality, or a guard. 
The result (SAT or UNSAT) of the final \texttt{check-sat} command in
the translation is then decoded.

@@

\vspace{-5mm}
\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} how to prove that they are bisimilar.

@@

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=0.9\linewidth]{ActaXFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{3.5cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{\{\xrightarrow{a1}_P\}\\ a1\neq\delta(x)}
    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{
                        \{\xrightarrow{a2}_Q\},\\a2\neq\delta(x)
                        }
    {\ostate{10} \xrightarrow{a2} \ostate{10}}
    \end{eqnarray*}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{4cm}
  \begin{eqnarray*}
    OT_4 & = \openrule{
                      \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{\{\xrightarrow{a3}_R\}
    	}
    {\ostate{11} \xrightarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``$P>>(Q>>R)$''}
  \label{schema:enable3bis}
\end{figure}

@@
